\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-07-01 paper/main.tex
.

\name{} introduces a number of novel

While the exploitation of ontology based features over PPI graphs was already examined in \citet{Trebacz2020} for gene expression analysis, our work is the first to investigate and apply this technique to DTI prediction. Further, \name{} is the first work to combine both ``bottom-up'' and ``top-down'' features.

>>>>

To the best of our knowledge, \name{} is the first DTI prediction
model that propagates ontology-based features of protein interaction
networks; while a similar approach of combining ontology embeddings
with interaction networks has previously been used for analyzing gene
expression \citet{Trebacz2020}, \name{} extends this method to DTI
prediction. Further, \name{} is novel in that it explicitly integrates
``bottom-up'' and ``top-down'' features using a graph representation
of interactions between proteins; this property of \name{} relies on
the ability to integrate heterogeneous features using graphs, and the
ability to exploit this graph through the use of graph neural
networks.
